---
title: "Client Satisfaction Report"
subtitle: "2019-2020 Survey Results"
date: "December 2019 (Survey 1)"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, out.width='90%')
pagebreak <- function() {
  if(knitr::is_latex_output())
    return("\\newpage")
  else
    return('<div style="page-break-before: always;" />')
}
```

```{r File open and setup, include=FALSE}
#
# Library setups
#

# Import libraries
library(tidyverse)
library(tidyr)
library(plyr)
library(dplyr)
library(caret)
library(ggplot2)
library(ggthemes)
library(extrafont)
library(scales)
library(reshape2)
library(expss)
library(grid)
library(gridExtra)
library(lattice)
library(janitor)
library(rmarkdown)
library(kableExtra)
library(googlesheets)
library(purrr)

################################################################################
#
# File open, cleanup, and set up for the analysis
#
################################################################################

#
# Download and open survey file
#

# Import and Open the data file / Establish the data set
data_filename <- gs_title("2019-2020 TSG Satisfaction Survey")
dat <- gs_read(data_filename, stringsAsFactors = FALSE)

#
# Clean data file to set vector names
#

dat <- rename(dat, replace = c("Timestamp" = "Surveyed",
                               "1A. TSG representatives are always able to understand my problems / needs. [Account Managers]" = "Q1A_AM",
                               "1A. TSG representatives are always able to understand my problems / needs. [Business Applications Support]" = "Q1A_BA",
                               "1A. TSG representatives are always able to understand my problems / needs. [B&MPS]" = "Q1A_BM",
                               "1A. TSG representatives are always able to understand my problems / needs. [Project Support / PMO]" = "Q1A_PS",
                               "1A. TSG representatives are always able to understand my problems / needs. [Service Desk]" = "Q1A_SD",
                               "1A. TSG representatives are always able to understand my problems / needs. [Vendor Managers]" = "Q1A_VM",
                               "1B. TSG representatives ask the right questions and listen to my input. [Account Managers]" = "Q1B_AM",
                               "1B. TSG representatives ask the right questions and listen to my input. [Business Applications Support]" = "Q1B_BA",
                               "1B. TSG representatives ask the right questions and listen to my input. [B&MPS]" = "Q1B_BM",
                               "1B. TSG representatives ask the right questions and listen to my input. [Project Support / PMO]" = "Q1B_PS",
                               "1B. TSG representatives ask the right questions and listen to my input. [Service Desk]" = "Q1B_SD",
                               "1B. TSG representatives ask the right questions and listen to my input. [Vendor Managers]" = "Q1B_VM",
                               "1C. TSG representatives stay in touch until my problems are resolved or my needs are met. [Account Managers]" = "Q1C_AM",
                               "1C. TSG representatives stay in touch until my problems are resolved or my needs are met. [Business Applications Support]" = "Q1C_BA",
                               "1C. TSG representatives stay in touch until my problems are resolved or my needs are met. [B&MPS]" = "Q1C_BM",
                               "1C. TSG representatives stay in touch until my problems are resolved or my needs are met. [Project Support / PMO]" = "Q1C_PS",
                               "1C. TSG representatives stay in touch until my problems are resolved or my needs are met. [Service Desk]" = "Q1C_SD",
                               "1C. TSG representatives stay in touch until my problems are resolved or my needs are met. [Vendor Managers]" = "Q1C_VM",
                               "2A. TSG representatives always have the knowledge to address my needs. [Account Managers]" = "Q2A_AM",
                               "2A. TSG representatives always have the knowledge to address my needs. [Business Applications Support]" = "Q2A_BA",
                               "2A. TSG representatives always have the knowledge to address my needs. [B&MPS]" = "Q2A_BM",
                               "2A. TSG representatives always have the knowledge to address my needs. [Project Support / PMO]" = "Q2A_PS",
                               "2A. TSG representatives always have the knowledge to address my needs. [Service Desk]" = "Q2A_SD",
                               "2A. TSG representatives always have the knowledge to address my needs. [Vendor Managers]" = "Q2A_VM",
                               "2B.  TSG representatives address my needs completely and professionally. [Account Managers]" = "Q2B_AM",
                               "2B.  TSG representatives address my needs completely and professionally. [Business Applications Support]" = "Q2B_BA",
                               "2B.  TSG representatives address my needs completely and professionally. [B&MPS]" = "Q2B_BM",
                               "2B.  TSG representatives address my needs completely and professionally. [Project Support / PMO]" = "Q2B_PS",
                               "2B.  TSG representatives address my needs completely and professionally. [Service Desk]" = "Q2B_SD",
                               "2B.  TSG representatives address my needs completely and professionally. [Vendor Managers]" = "Q2B_VM",
                               "3. TSG representatives always resolve my needs or problems within my required timeframes. [Account Managers]" = "Q3_AM",
                               "3. TSG representatives always resolve my needs or problems within my required timeframes. [Business Applications Support]" = "Q3_BA",
                               "3. TSG representatives always resolve my needs or problems within my required timeframes. [B&MPS]" = "Q3_BM",
                               "3. TSG representatives always resolve my needs or problems within my required timeframes. [Project Support / PMO]" = "Q3_PS",
                               "3. TSG representatives always resolve my needs or problems within my required timeframes. [Service Desk]" = "Q3_SD",
                               "3. TSG representatives always resolve my needs or problems within my required timeframes. [Vendor Managers]" = "Q3_VM",
                               "What additional comments do you have for TSG (pro or con) that might help us serve you better?" = "Comments",
                               "Email Address" = "Email"))

#
# Convert time stamps to survey names
#

# Strip off the clock time and leave just the date
dat$Surveyed <-gsub(" .*","",dat$Surveyed)

# Set survey groupings
for(i in 1:length(dat$Surveyed)) {
  if(str_detect(dat$Surveyed[i], "2019")) {
    dat$Surveyed[i] <- "1F19"
  }
  if(dat$Surveyed[i] != "1F19" & dat$Surveyed[i] > "1/1/2020" & dat$Surveyed[i] < "4/1/2020") {
    dat$Surveyed[i] <- "2W20"
  }
  if(dat$Surveyed[i] != "1F19" & dat$Surveyed[i] > "4/1/2020" & dat$Surveyed[i] < "6/30/2020") {
    dat$Surveyed[i] <- "3S20"
  }
  if(dat$Surveyed[i] != "1F19" & dat$Surveyed[i] > "7/1/2020" & dat$Surveyed[i] < "9/30/2020") {
    dat$Surveyed[i] <- "4S20"
  }
}

Q1_responses <- nrow(dat %>% filter(dat$Surveyed =="1F19"))
Q2_responses <- nrow(dat %>% filter(dat$Surveyed =="2W20"))
Q3_responses <- nrow(dat %>% filter(dat$Surveyed =="3S20"))
Q4_responses <- nrow(dat %>% filter(dat$Surveyed =="4S20"))

# Remove rows below the actual data / Remove Comments
dat <- subset(dat, dat[ , 1] != "") %>% select(-Comments, -Email) 

# Convert text to numbers
dat[dat == "1 - Strongly Disagree"]  <- 1
dat[dat == "4 - Disagree"]           <- 4
dat[dat == "7 - Agree"]              <- 7
dat[dat == "10 - Strongly Agree"]    <- 10
dat[dat == "NA or Do Not Use"]       <- 0
dat[is.na(dat)]                      <- 0
dat[dat == "0"]                      <- 0
dat[dat == ""]                       <- 0

################################################################################
#
# Create dataframes for reporting
#
################################################################################

# Create the dataframes to hold all the results
res_df     <- data.frame(Qtr = 1:6,   Group = 1:6,   Question = 1:6,   Avg = 1:6)

res_df_am  <- data.frame(Qtr = 1:6,   Group = 1:6,   Question = 1:6,   Avg = 1:6)
res_df_ba  <- data.frame(Qtr = 1:6,   Group = 1:6,   Question = 1:6,   Avg = 1:6)
res_df_bm  <- data.frame(Qtr = 1:6,   Group = 1:6,   Question = 1:6,   Avg = 1:6)
res_df_ps  <- data.frame(Qtr = 1:6,   Group = 1:6,   Question = 1:6,   Avg = 1:6)
res_df_sd  <- data.frame(Qtr = 1:6,   Group = 1:6,   Question = 1:6,   Avg = 1:6)
res_df_vm  <- data.frame(Qtr = 1:6,   Group = 1:6,   Question = 1:6,   Avg = 1:6)

grp_x_qtr  <- list(res_df_am, res_df_ba, res_df_bm, res_df_ps, res_df_sd, res_df_vm)
full_year  <- list(Q1 = grp_x_qtr, Q2 = grp_x_qtr, Q3 = grp_x_qtr, Q4 = grp_x_qtr)
groups <- c("AM", "BA", "BM", "PS", "SD", "VM")
questions <- c("1A", "1B", "1C", "2A", "2B", "3x")

#-------------------------------------------------------------------------------
#
# Work through each breakdown - by quarter, then group, then question
#
#-------------------------------------------------------------------------------

am_results  <- transform(dat[c(1, 2, 8,14,20,26,32)])
ba_results  <- transform(dat[c(1, 3, 9,15,21,27,33)])
bm_results  <- transform(dat[c(1, 4,10,16,22,28,34)])
ps_results  <- transform(dat[c(1, 5,11,17,23,29,35)])
sd_results  <- transform(dat[c(1, 6,12,18,24,30,36)])
vm_results  <- transform(dat[c(1, 7,13,19,25,31,37)])

results_list <- list(am_results, ba_results, bm_results, ps_results, sd_results, vm_results)

#
# Process each group, quarter by quarter
#

# Establish the quarter
for(a in 1:length(unique(dat$Surveyed))) {
  quarter <- unique(dat$Surveyed)[a]
  
  # Outer loop to establish the group and data
  for(i in 1:length(groups)) {
    group      <- groups[i]
    group_data <- as.data.frame(results_list[i])
    group_data <- group_data %>% filter(Surveyed == quarter)
    group_data <- group_data %>% select(-Surveyed)
  
   # Establish the number of responses in this group
    x <- nrow(group_data)
    
    # Create a dataframe to hold the six answers as numberics
    new_df <- data.frame(Q1A = 1:x, Q1B = 1:x, Q1C = 1:x, Q2A = 1:x, Q2B = 1:x, Q3x = 1:x)
    
    # Next loop to write the numeric values to the new dataframe
    for(j in 1:x) {
      for(k in 1:6) {
        if(group_data[j,k] == "0") {
          new_df[j,k] = 0
          }
        if(group_data[j,k] == "1") {
          new_df[j,k] = 1
        }
        if(group_data[j,k] == "2") {
          new_df[j,k] = 2
        }
        if(group_data[j,k] == "3") {
          new_df[j,k] = 3
        }
        if(group_data[j,k] == "4") {
          new_df[j,k] = 4
        }
        if(group_data[j,k] == "5") {
          new_df[j,k] = 5
        }
        if(group_data[j,k] == "6") {
          new_df[j,k] = 6
        }
        if(group_data[j,k] == "7") {
          new_df[j,k] = 7
        }
        if(group_data[j,k] == "8") {
          new_df[j,k] = 8
        }
        if(group_data[j,k] == "9") {
          new_df[j,k] = 9
        }
        if(group_data[j,k] == "10") {
          new_df[j,k] = 10
        }
      }
    }
    for(m in 1:6) {
      
      # Clear out the NR and DNUs
      y <- new_df[m] == 0
      z <- length(y[y == TRUE])
      
      # Calculate the mean
      mean_new_df <- round(sum(new_df[m]) / (x - z), digits = 2)
      
      # write the results to the dataframe
      res_df[m,1]  <- quarter
      res_df[m,2]  <- group
      res_df[m,3]  <- questions[m]
      res_df[m,4]  <- mean_new_df
    }
    # Now we have the entire quarter for each group
    grp_x_qtr[[i]] <- res_df
  }
  # Until I can figure out how to access parts of a list by indexing alone, we 
  # loop through to make sure the results for the quarter to to the right place
  if(a == 1) {
    full_year$Q1 <- grp_x_qtr
  }
  if(a == 2) {
    full_year$Q2 <- grp_x_qtr
  }
  if(a == 3) {
    full_year$Q3 <- grp_x_qtr
  }
  if(a == 4) {
    full_year$Q4 <- grp_x_qtr
  }
}

```

**Introduction to Quarter 1 Results (Fall, 2019)**

The 2019-2020 OCIO customer sat survey builds on the lessons learned from the four surveys done during 2018-2019, and focuses on 6 questions grouped into 3 categories:

Empathy

  * 1A TSG representatives are always able to understand my problems / needs.
  * 1B TSG representatives ask the right questions and listen to my input.
  * 1C TSG representatives stay in touch until my problems are resolved or my needs are met.
  
Expertise

  * 2A TSG representatives always have the knowledge to address my needs.
  * 2B TSG representatives address my needs completely and professionally. 
  
Efficiency

  * 3x TSG representatives always resolve my needs or problems within my required timeframes

These questions were sent out to a randomly selected sample of 25% of the entire TMC population. By randomly selecting responders each time, we should achieve more statistically significant results. By running the survey 4 times over the course of the year (that is, but not surveying the entire population once), it should make it possible to see if any corrections or improvements made along the way have improved the overall scores. Responses were only counted where a 1-10 value was given; that is, missing, "N/A" or "Do Not Use" responses were not figured into the averages.

The data is shown for OCIO overall and with group and question breakouts:

* Overall results show how OCIO did by group and by question
* Group breakouts show each group scored by question
* Question breakouts show each question scored by group

General Observations

* Scores were clustered; that is, they were closely grouped between a low of 7.65 and a high of 9.17 (a span of 1.52)  
* The closeness of the scores / range makes it difficult to discern major differences between strengths and weaknesses  
* However, the points below *may* be useful for the management team to consider  
  * Questions  
    * Question 1A (Always understands my problem) at an average of 8.64 was the highest scoring question overall. B&MPS and the Service Desk and B&MPS scored higher and Project Support and Business Analysts scored lower - but the range was only 0.87.  
    * Question 3 (Efficiency) at 8.19 was the lowest scoring question overall Scores were higher for B&MPS and the Service desk; the other groups were clustered within 0.20 points of each other. 
  * Groups
    * The highest and lowest were separated by a small margin (1.09 points)  
    * B&MPS and the Service Desk were the highest performing groups, tying at a 8.98 overall average score  
    * B&MPS scored high on expertise (questions 2A and 2B) and was strong overall (scores were highly clustered)  
    * The Service Desk scored higher on Empathy (questions 1A-1C) but lower on Knowledge (2A)
    * Project Support scored lower overall (7.89) with a weakness in Knowledge but strength in Empathy  
    * Account Managers, Business Analysts, and Vendor Managers formed a middle tier, clustered between 8.19 and 8.39 (0.20 points); they scored lowest on question 3 (efficiency)  
      
What these Results (May) Imply

* There is general strength in all areas sampled - scores ranged between 8.19 and 8.64 overall (a range of only 0.45), which is relatively tight. Empathy appears to be a strength to build on
* Individual scores in expertise were mixed and may suggest a need to focus on the perceptions around those groups scoring lower (that is, all but B&MPS and the Service Desk)
* Similarly, except for B&MPS and the Service Desk, there may be an opportunity to improve on Efficiency (speed) across all the groups

`r pagebreak()`

**Summary Charts**

Total Responses for Q1: `r Q1_responses`

```{r Graphics - Summaries, echo=FALSE}
################################################################################
#
# Graphics 
#
################################################################################

#
# Set up dataframe to collect the mean for each question by group
#

fy_df <- data.frame(Qtr = 1:24, Group = 1:24, Avg = 1:24)

# Populate the first two colums
fy_df[ 1:6, 1]  <- unique(dat$Surveyed)[1]
fy_df[ 7:12,1]  <- unique(dat$Surveyed)[2]
fy_df[13:18,1]  <- unique(dat$Surveyed)[3]
fy_df[19:24,1]  <- unique(dat$Surveyed)[4]

fy_df[ 1:6, 2] <- t(groups)[ ,1:6]
fy_df[ 7:12,2] <- t(groups)[ ,1:6]
fy_df[13:18,2] <- t(groups)[ ,1:6]
fy_df[19:24,2] <- t(groups)[ ,1:6]

#
# Set up the dataframe to collect data for summary of questions
#

qs_df <- data.frame(Group = 1:24, Q1A = 1:24, Q1B = 1:24, Q1C = 1:24, Q2A = 1:24, Q2B = 1:24, Q3x = 1:24)
qs_df[ 1:6, 1] <- t(groups)[ ,1:6]
qs_df[ 7:12,1] <- t(groups)[ ,1:6]
qs_df[13:18,1] <- t(groups)[ ,1:6]
qs_df[19:24,1] <- t(groups)[ ,1:6]

#-------------------------------------------------------------------------------
#
# Part 1 - Quarterly Summaries
#    8 charts total (2 / quarter)
#
#    For each Quarter (4) Question Response Averages by group 
#    X = Group
#    Y = Average Score
#
#    For each quarter (4) Group Averages by Question
#    X = Question
#    Y - Average Score
#
#-------------------------------------------------------------------------------

#-------------------------------------------------------------------------------
#
#  Response Averages by Group
#
#-------------------------------------------------------------------------------

# Q1 Assemble data
gbq_q1_df <- fy_df %>% filter(Qtr == unique(dat$Surveyed)[1])
for(i in 1:6) {
  gbq_q1_df[i,3] <- round(mean(full_year$Q1[[i]]$Avg), digits = 2)
}

# Q1 Build plot
gbq_q1_bar <- ggplot() +
  geom_bar(aes(x = Group, y = Avg, fill = "red"),
           data = gbq_q1_df, stat = "identity") +
  geom_text(data = gbq_q1_df, aes(x = Group, y = Avg, label = Avg), 
            vjust = 1.5, color = "black", size = 4) + 
  theme(legend.position = "none") +
  labs(title = "Response Averages", subtitle = "Q1 (Fall 2019) - By Group")     

#-------------------------------------------------------------------------------
#
#  Response Averages by Question
#
#-------------------------------------------------------------------------------

# Q1 Gather data
qbq_q1_df <- data.frame(Question = 1:6, Avg = 1:6)

x = 0
for(i in 1:6) {
  qbq_q1_df[i,1] <- questions[i]
  for(j in 1:6) {
    x <- x + full_year$Q1[[j]]$Avg[i]
  }
  x <- x / 6
  qbq_q1_df[i,2] <- round(x, digits = 2)
  x = 0
}

# Q1 Build plot
qbq_q1_bar <- ggplot() +
  geom_bar(aes(x = Question, y = Avg, fill = "red"),
           data = qbq_q1_df, stat = "identity") +
  geom_text(data = qbq_q1_df, aes(x = Question, y = Avg, label = Avg), 
            vjust = 1.5, color = "black", size = 4) + 
  theme(legend.position = "none") +
  labs(title = "Response Averages", subtitle = "Q1 (Fall 2019) - By Question") 

grid.arrange(gbq_q1_bar, qbq_q1_bar, ncol = 2)

```

`r pagebreak()`

**Group Breakouts**

```{r Graphics - Group Breakouts - 1, echo=FALSE}
#-------------------------------------------------------------------------------
#
# Part 2 - Quarterly Summaries by Group
#    24 charts
#    For each Quarter, 1 chart per group for Questions 1-6
#    X = Question
#    Y - Average Score
#
#-------------------------------------------------------------------------------

#-------------------------------------------------------------------------------
#  Quarter 1
#    One chart per group
#-------------------------------------------------------------------------------

#
# Account Managers
#

grp_df <- as.data.frame(full_year$Q1[1])
ms <- round(mean(grp_df$Avg), digits = 2)
fy_df[1,2] <- "AM"
fy_df[1,3] <- ms

am_bar_Q1 <- ggplot() +
  geom_bar(aes(x = Question, y = Avg, fill = "red"),
           data = grp_df, stat = "identity") +
  geom_text(data = grp_df, aes(x = Question, y = Avg, label = Avg), 
            vjust = 1.5, color = "black", size = 4) + 
  theme(legend.position = "none") +
  labs(title = "Account Managers", subtitle = paste("Q1 (Fall 2019) Average Score =",ms))

#
# business Analysts
#

grp_df <- as.data.frame(full_year$Q1[2])
ms <- round(mean(grp_df$Avg), digits = 2)
fy_df[2,2] <- "BA"
fy_df[2,3] <- ms

ba_bar_Q1 <- ggplot() +
  geom_bar(aes(x = Question, y = Avg, fill = "red"),
           data = grp_df, stat = "identity") +
  geom_text(data = grp_df, aes(x = Question, y = Avg, label = Avg), 
            vjust = 1.5, color = "black", size = 4) + 
  theme(legend.position = "none") +
  labs(title = "Business Analysts", subtitle = paste("Q1 (Fall 2019) Average Score =",ms))

#
# B&MPS
#

grp_df <- as.data.frame(full_year$Q1[3])
ms <- round(mean(grp_df$Avg), digits = 2)
fy_df[3,2] <- "B&MPS"
fy_df[3,3] <- ms

bm_bar_Q1 <- ggplot() +
  geom_bar(aes(x = Question, y = Avg, fill = "red"),
           data = grp_df, stat = "identity") +
  geom_text(data = grp_df, aes(x = Question, y = Avg, label = Avg), 
            vjust = 1.5, color = "black", size = 4) + 
  theme(legend.position = "none") +
  labs(title = "B&MPS", subtitle = paste("Q1 (Fall 2019) Average Score =",ms))

#
# Project Support
#

grp_df <- as.data.frame(full_year$Q1[4])
ms <- round(mean(grp_df$Avg), digits = 2)
fy_df[4,2] <- "PS"
fy_df[4,3] <- ms

ps_bar_Q1 <- ggplot() +
  geom_bar(aes(x = Question, y = Avg, fill = "red"),
           data = grp_df, stat = "identity") +
  geom_text(data = grp_df, aes(x = Question, y = Avg, label = Avg), 
            vjust = 1.5, color = "black", size = 4) + 
  theme(legend.position = "none") +
  labs(title = "Project Support", subtitle = paste("Q1 (Fall 2019) Average Score =",ms))

#
# Service Desk
#

grp_df <- as.data.frame(full_year$Q1[5])
ms <- round(mean(grp_df$Avg), digits = 2)
fy_df[5,2] <- "SD"
fy_df[5,3] <- ms

sd_bar_Q1 <- ggplot() +
  geom_bar(aes(x = Question, y = Avg, fill = "red"),
           data = grp_df, stat = "identity") +
  geom_text(data = grp_df, aes(x = Question, y = Avg, label = Avg), 
            vjust = 1.5, color = "black", size = 4) + 
  theme(legend.position = "none") +
  labs(title = "Service Desk", subtitle = paste("Q1 (Fall 2019) Average Score =",ms))

#
# Vendor Managers
#

grp_df <- as.data.frame(full_year$Q1[6])
ms <- round(mean(grp_df$Avg), digits = 2)
fy_df[6,2] <- "VM"
fy_df[6,3] <- ms

vm_bar_Q1 <- ggplot() +
  geom_bar(aes(x = Question, y = Avg, fill = "red"),
           data = grp_df, stat = "identity") +
  geom_text(data = grp_df, aes(x = Question, y = Avg, label = Avg), 
            vjust = 1.5, color = "black", size = 4) + 
  theme(legend.position = "none") +
  labs(title = "Vendor Managers", subtitle = paste("Q1 (Fall 2019) Average Score =",ms))

grid.arrange(am_bar_Q1, ba_bar_Q1, ncol = 2)
grid.arrange(bm_bar_Q1, ps_bar_Q1, ncol = 2)
```

`r pagebreak()`

```{r Graphics - Group Breakouts - 2, echo=FALSE}
grid.arrange(sd_bar_Q1, vm_bar_Q1, ncol = 2)
```

`r pagebreak()`

**Question Breakouts**

```{r Graphics - Question Breakouts - 1, echo=FALSE}
#-------------------------------------------------------------------------------
#
# Part 3 - Quarterly Summaries by Question
#    24 charts
#    For each Quarter, 1 chart per Question for Groups 1-6
#    X = Question
#    Y - Average Score
#
#-------------------------------------------------------------------------------

#-------------------------------------------------------------------------------
#  Quarter 1
#    One chart per Question
#    For each of the 6 questions, X = Group, Y = Avg
#-------------------------------------------------------------------------------

#
# Question 1A
#

# Q1 Gather data
qbq_q1_q1a_df <- transform(as.data.frame(full_year$Q1)[c(1,3, 2,4,6,8,10,12,14,16,18,20,22,24)])
Q1_Q1A <- data.frame(Group = 1:6, Avg = 1:6)

Q1_Q1A[1,  1] <- qbq_q1_q1a_df[1,  3]
Q1_Q1A[1,  2] <- qbq_q1_q1a_df[1,  4]
Q1_Q1A[2,  1] <- qbq_q1_q1a_df[1,  5]
Q1_Q1A[2,  2] <- qbq_q1_q1a_df[1,  6]
Q1_Q1A[3,  1] <- qbq_q1_q1a_df[1,  7]
Q1_Q1A[3,  2] <- qbq_q1_q1a_df[1,  8]
Q1_Q1A[4,  1] <- qbq_q1_q1a_df[1,  9]
Q1_Q1A[4,  2] <- qbq_q1_q1a_df[1, 10]
Q1_Q1A[5,  1] <- qbq_q1_q1a_df[1, 11]
Q1_Q1A[5,  2] <- qbq_q1_q1a_df[1, 12]
Q1_Q1A[6,  1] <- qbq_q1_q1a_df[1, 13]
Q1_Q1A[6,  2] <- qbq_q1_q1a_df[1, 14]

Q1_Q1A_ms <- round(mean(Q1_Q1A[2]), digits = 2)
  
# Q1 Build plot
Q1_Q1A_bar <- ggplot() +
  geom_bar(aes(x = Group, y = Avg, fill = "red"),
           data = Q1_Q1A, stat = "identity") +
  geom_text(data = Q1_Q1A, aes(x = Group, y = Avg, label = Avg), 
            vjust = 1.5, color = "black", size = 4) + 
  theme(legend.position = "none") +
  labs(title = "Question Q1A", subtitle = paste("Q1 (Fall 2019) Averages by Group - Overall Average =", Q1_Q1A_ms)) 


Q1_Q1A_bar

#
# Question 1B
#

# Q1 Gather data
qbq_q1_q1b_df <- transform(as.data.frame(full_year$Q1)[c(1,3, 2,4,6,8,10,12,14,16,18,20,22,24)])
Q1_Q1B <- data.frame(Group = 1:6, Avg = 1:6)

Q1_Q1B[1,  1] <- qbq_q1_q1b_df[2,  3]
Q1_Q1B[1,  2] <- qbq_q1_q1b_df[2,  4]
Q1_Q1B[2,  1] <- qbq_q1_q1b_df[2,  5]
Q1_Q1B[2,  2] <- qbq_q1_q1b_df[2,  6]
Q1_Q1B[3,  1] <- qbq_q1_q1b_df[2,  7]
Q1_Q1B[3,  2] <- qbq_q1_q1b_df[2,  8]
Q1_Q1B[4,  1] <- qbq_q1_q1b_df[2,  9]
Q1_Q1B[4,  2] <- qbq_q1_q1b_df[2, 10]
Q1_Q1B[5,  1] <- qbq_q1_q1b_df[2, 11]
Q1_Q1B[5,  2] <- qbq_q1_q1b_df[2, 12]
Q1_Q1B[6,  1] <- qbq_q1_q1b_df[2, 13]
Q1_Q1B[6,  2] <- qbq_q1_q1b_df[2, 14]

Q1_Q1B_ms <- round(mean(Q1_Q1B[2]), digits = 2)

# Q1 Build plot
Q1_Q1B_bar <- ggplot() +
  geom_bar(aes(x = Group, y = Avg, fill = "red"),
           data = Q1_Q1B, stat = "identity") +
  geom_text(data = Q1_Q1B, aes(x = Group, y = Avg, label = Avg), 
            vjust = 1.5, color = "black", size = 4) + 
  theme(legend.position = "none") +
  labs(title = "Question Q1B", subtitle = paste("Q1 (Fall 2019) Averages by Group - Overall Average =", Q1_Q1B_ms)) 


Q1_Q1B_bar
```

`r pagebreak()`

```{r Graphics - Question Breakouts - 2, echo=FALSE}
#
# Question 1c
#

# Q1 Gather data
qbq_q1_q1c_df <- transform(as.data.frame(full_year$Q1)[c(1,3, 2,4,6,8,10,12,14,16,18,20,22,24)])
Q1_Q1C <- data.frame(Group = 1:6, Avg = 1:6)

Q1_Q1C[1,  1] <- qbq_q1_q1c_df[3,  3]
Q1_Q1C[1,  2] <- qbq_q1_q1c_df[3,  4]
Q1_Q1C[2,  1] <- qbq_q1_q1c_df[3,  5]
Q1_Q1C[2,  2] <- qbq_q1_q1c_df[3,  6]
Q1_Q1C[3,  1] <- qbq_q1_q1c_df[3,  7]
Q1_Q1C[3,  2] <- qbq_q1_q1c_df[3,  8]
Q1_Q1C[4,  1] <- qbq_q1_q1c_df[3,  9]
Q1_Q1C[4,  2] <- qbq_q1_q1c_df[3, 10]
Q1_Q1C[5,  1] <- qbq_q1_q1c_df[3, 11]
Q1_Q1C[5,  2] <- qbq_q1_q1c_df[3, 12]
Q1_Q1C[6,  1] <- qbq_q1_q1c_df[3, 13]
Q1_Q1C[6,  2] <- qbq_q1_q1c_df[3, 14]

Q1_Q1C_ms <- round(mean(Q1_Q1C[2]), digits = 2)

# Q1 Build plot
Q1_Q1C_bar <- ggplot() +
  geom_bar(aes(x = Group, y = Avg, fill = "red"),
           data = Q1_Q1C, stat = "identity") +
  geom_text(data = Q1_Q1C, aes(x = Group, y = Avg, label = Avg), 
            vjust = 1.5, color = "black", size = 4) + 
  theme(legend.position = "none") +
  labs(title = "Question Q1C", subtitle = paste("Q1 (Fall 2019) Averages by Group - Overall Average =", Q1_Q1C_ms)) 


Q1_Q1C_bar
```

`r pagebreak()`

```{r Graphics - Question Breakouts -3, echo=FALSE}
#
# Question 2A
#

# Q1 Gather data
qbq_q1_q2a_df <- transform(as.data.frame(full_year$Q1)[c(1,3, 2,4,6,8,10,12,14,16,18,20,22,24)])
Q1_Q2A <- data.frame(Group = 1:6, Avg = 1:6)

Q1_Q2A[1,  1] <- qbq_q1_q2a_df[4,  3]
Q1_Q2A[1,  2] <- qbq_q1_q2a_df[4,  4]
Q1_Q2A[2,  1] <- qbq_q1_q2a_df[4,  5]
Q1_Q2A[2,  2] <- qbq_q1_q2a_df[4,  6]
Q1_Q2A[3,  1] <- qbq_q1_q2a_df[4,  7]
Q1_Q2A[3,  2] <- qbq_q1_q2a_df[4,  8]
Q1_Q2A[4,  1] <- qbq_q1_q2a_df[4,  9]
Q1_Q2A[4,  2] <- qbq_q1_q2a_df[4, 10]
Q1_Q2A[5,  1] <- qbq_q1_q2a_df[4, 11]
Q1_Q2A[5,  2] <- qbq_q1_q2a_df[4, 12]
Q1_Q2A[6,  1] <- qbq_q1_q2a_df[4, 13]
Q1_Q2A[6,  2] <- qbq_q1_q2a_df[4, 14]

Q1_Q2A_ms <- round(mean(Q1_Q2A[2]), digits = 2)

# Q1 Build plot
Q1_Q2A_bar <- ggplot() +
  geom_bar(aes(x = Group, y = Avg, fill = "red"),
           data = Q1_Q2A, stat = "identity") +
  geom_text(data = Q1_Q2A, aes(x = Group, y = Avg, label = Avg), 
            vjust = 1.5, color = "black", size = 4) + 
  theme(legend.position = "none") +
  labs(title = "Question Q2A", subtitle = paste("Q1 (Fall 2019) Averages by Group - Overall Average =", Q1_Q2A_ms)) 


Q1_Q2A_bar

#
# Question 2B
#

# Q1 Gather data
qbq_q1_q2b_df <- transform(as.data.frame(full_year$Q1)[c(1,3, 2,4,6,8,10,12,14,16,18,20,22,24)])
Q1_Q2B <- data.frame(Group = 1:6, Avg = 1:6)

Q1_Q2B[1,  1] <- qbq_q1_q2b_df[5,  3]
Q1_Q2B[1,  2] <- qbq_q1_q2b_df[5,  4]
Q1_Q2B[2,  1] <- qbq_q1_q2b_df[5,  5]
Q1_Q2B[2,  2] <- qbq_q1_q2b_df[5,  6]
Q1_Q2B[3,  1] <- qbq_q1_q2b_df[5,  7]
Q1_Q2B[3,  2] <- qbq_q1_q2b_df[5,  8]
Q1_Q2B[4,  1] <- qbq_q1_q2b_df[5,  9]
Q1_Q2B[4,  2] <- qbq_q1_q2b_df[5, 10]
Q1_Q2B[5,  1] <- qbq_q1_q2b_df[5, 11]
Q1_Q2B[5,  2] <- qbq_q1_q2b_df[5, 12]
Q1_Q2B[6,  1] <- qbq_q1_q2b_df[5, 13]
Q1_Q2B[6,  2] <- qbq_q1_q2b_df[5, 14]

Q1_Q2B_ms <- round(mean(Q1_Q2B[2]), digits = 2)

# Q1 Build plot
Q1_Q2B_bar <- ggplot() +
  geom_bar(aes(x = Group, y = Avg, fill = "red"),
           data = Q1_Q2B, stat = "identity") +
  geom_text(data = Q1_Q2B, aes(x = Group, y = Avg, label = Avg), 
            vjust = 1.5, color = "black", size = 4) + 
  theme(legend.position = "none") +
  labs(title = "Question Q2B", subtitle = paste("Q1 (Fall 2019) Averages by Group - Overall Average =", Q1_Q2B_ms)) 


Q1_Q2B_bar
```

`r pagebreak()`

```{r Graphics - Question Breakouts - 4, echo=FALSE}
#
# Question 3x
#

# Q1 Gather data
qbq_q1_q3x_df <- transform(as.data.frame(full_year$Q1)[c(1,3, 2,4,6,8,10,12,14,16,18,20,22,24)])
Q1_Q3x <- data.frame(Group = 1:6, Avg = 1:6)

Q1_Q3x[1,  1] <- qbq_q1_q3x_df[6,  3]
Q1_Q3x[1,  2] <- qbq_q1_q3x_df[6,  4]
Q1_Q3x[2,  1] <- qbq_q1_q3x_df[6,  5]
Q1_Q3x[2,  2] <- qbq_q1_q3x_df[6,  6]
Q1_Q3x[3,  1] <- qbq_q1_q3x_df[6,  7]
Q1_Q3x[3,  2] <- qbq_q1_q3x_df[6,  8]
Q1_Q3x[4,  1] <- qbq_q1_q3x_df[6,  9]
Q1_Q3x[4,  2] <- qbq_q1_q3x_df[6, 10]
Q1_Q3x[5,  1] <- qbq_q1_q3x_df[6, 11]
Q1_Q3x[5,  2] <- qbq_q1_q3x_df[6, 12]
Q1_Q3x[6,  1] <- qbq_q1_q3x_df[6, 13]
Q1_Q3x[6,  2] <- qbq_q1_q3x_df[6, 14]

Q1_Q3x_ms <- round(mean(Q1_Q3x[2]), digits = 2)

# Q1 Build plot
Q1_Q3x_bar <- ggplot() +
  geom_bar(aes(x = Group, y = Avg, fill = "red"),
           data = Q1_Q3x, stat = "identity") +
  geom_text(data = Q1_Q3x, aes(x = Group, y = Avg, label = Avg), 
            vjust = 1.5, color = "black", size = 4) + 
  theme(legend.position = "none") +
  labs(title = "Question 3x", subtitle = paste("Q1 (Fall 2019) Averages by Group - Overall Average =", Q1_Q3x_ms)) 

Q1_Q3x_bar

#--------------------------------------------------------------------
#
# End
#
#--------------------------------------------------------------------
```


[End of Report]
